---
title: "Strategy, Leadership, and Narratives -- Data Visualization for Policy Change"
output:
  ioslides_presentation: default
---

## R Markdown
Opinions about data visualization are everywhere and quick search online reveals thousands of resources to learn how to draw bar graphs and when a scatter plot might be effective. While getting the technical details right is important, it is merely the a necessary, but not sufficient, condition for driving change. In order to effectively use data in a decision making context, analysts must focus on knowing their audience, knowing the decision space, and leading their audience toward constructive engagement with the data. Using examples from senior leadership discussions at the Wisconsin Department of Public Instruction, this talk will explore how to build capacity in an audience and empower them to make decisions informed by analytics. A particular focus will be taken on the deliberate design choices an analyst must confront in order construct visualizations that are accessible and invite discussion. This includes strategies such as simulation, counterfactual modeling, and selection of context cues to bring the data into a familiar frame for the audience. The session will conclude with a brief discussion of practical advice on technologies, formats, and presentation techniques for different audience types.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

